%====================================================================================
%  single-FlexionSimToReal.tex  —  Flexion Robotics: Robotics Engineer, Modeling & Sim-to-Real
%  Zürich, Switzerland
%  Seeded from src/single-ref.tex (canonical seed). Do NOT seed from archive/* or master.tex.
%====================================================================================

\documentclass[letterpaper, 11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{vwcol}
\usepackage{comment}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=black,
	citecolor=black,
	urlcolor=Blue,
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% VSPACE VARIABLES (PRIMARY spacing control) — tune ALL layout spacing here, never edit
% the raw \vspace values inline. 18 canonical names, categorized by document section, with
% cross-section macro vars in Global/Shared first. To fit one page, make values MORE
% negative here (start with \vListEnd) — never touch margins or font. Copies of this seed
% inherit these names; keep the names identical across all single-* resumes.

% --- Global / Shared (drive macros used across every section) ---
\newcommand{\vSectionBefore}{-6pt} % space before each \section title
\newcommand{\vSectionRule}{-5pt}   % space after the blue section titlerule
\newcommand{\vTableRowSep}{-2pt}   % row strut between title/subtitle rows in resumeSubheading
\newcommand{\vItemTop}{-2pt}       % tightening atop resumeItem / subheading / project heading
\newcommand{\vSubheadingEnd}{-12pt}% space after a resumeSubheading block
\newcommand{\vSubItem}{-4pt}       % space after a resumeSubItem
\newcommand{\vListStart}{-0.3em}   % space before an item list start (resumeItemListStart / education list)
\newcommand{\vListEnd}{-10pt}      % space after resumeItemListEnd <- tighten THIS first if a real resume spills to page 2
\newcommand{\vListGroupEnd}{-1.5em}% space after resumeSubHeadingListEnd

% --- Header ---
\newcommand{\vHeadingName}{3pt}    % space under the name in the header
\newcommand{\vHeadingEnd}{-8pt}    % space after the header block

% --- Summary (not used in this resume) ---
\newcommand{\vSummaryTop}{2pt}
\newcommand{\vSummaryEnd}{-6pt}

% --- Education ---
\newcommand{\vEduSep}{0pt}         % space between education entries (0pt = adjacent)
\newcommand{\vEduItemSep}{-0.3em}  % itemsep between Education achievement bullets
\newcommand{\vEduSkills}{-0.7em}   % space before the Skills line

% --- Technical Projects ---
\newcommand{\vProjectEnd}{-20pt}   % space after a resumeProjectHeading block

% --- Publications ---
\newcommand{\vPubSep}{-5pt}        % itemsep between Publications entries

% Sections formatting
\titleformat{\section}{ \vspace{\vSectionBefore}\scshape\raggedright\large\bfseries }{}{0em}{}[
\color{Blue}{}
\titlerule
\vspace{\vSectionRule}
]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{ \item\small{ {#1 \vspace{\vItemTop}} } }

\newcommand{\resumeSubheading}[4]{
\vspace{\vItemTop}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}       & {\small #2} \\
     [\vTableRowSep]
	\textit{{\small#3}} & \textit{\small #4} \\
\end{tabular*}
\vspace{\vSubheadingEnd}
}

\newcommand{\resumeProjectHeading}[2]{
\vspace{\vItemTop}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}  & {\small #2} \\
\end{tabular*}
\vspace{\vProjectEnd}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}
\vspace{\vSubItem}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{\vListGroupEnd}}
\newcommand{\resumeItemListStart}{\vspace{\vListStart}\begin{itemize}[leftmargin=0.25in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{\vListEnd}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Gawtam Chithra Ramesh} \\
    \vspace{\vHeadingName}
    \small
    { \href{tel:+46764518589}{{\faMobile*} \textcolor{black}{(+46) 76541-8589}} ~
    \href{mailto:gawtamcr3@gmail.com}{{\faPaperPlane} \textcolor{black}{gawtamcr3@gmail.com}} ~
    \href{https://linkedin.com/in/gawtamcr/}{{\faLinkedinIn} \textcolor{black}{Gawtam C R}} ~
    \href{https://github.com/gawtamcr}{{\faGithub} \textcolor{black}{gawtamcr}} ~
    \href{https://gawtamcr.github.io/}{{\faGlobe} \textcolor{black}{Portfolio}} ~
    \href{https://maps.google.com/?q=Stockholm,Sweden}{{\faMapMarker*} \textcolor{black}{Stockholm, Sweden}}
    }
    \vspace{\vHeadingEnd}
\end{center}

%-----------EDUCATION-----------
\section{\color{Blue}Education}
    \resumeSubHeadingListStart
    \resumeSubheading{KTH Royal Institute of Technology}{Aug 2024 -- Jun 2026}{Master of Science in Systems, Controls, and Robotics \textnormal{(GPA 4.62/5.0)}}{Stockholm, Sweden}
    \vspace{\vEduSep}
    \resumeSubheading{Indian Institute of Technology Madras}{Aug 2019 -- Jul 2024}{Dual Degree (B.Tech Engineering Design and M.Tech Robotics) \textnormal{(GPA 7.9/10)}}{Chennai, India}
    \vspace{\vListStart}
    \small{
    \begin{itemize}[leftmargin=0.15in]
        \setlength{\itemsep}{\vEduItemSep}
        \item Awarded (among 30 of 800+) the IIT Madras \textbf{Young Research Fellowship} based on remarkable research potential.
        \item Secured \textbf{97.64} Percentile in JEE Advanced and \textbf{99.10} Percentile in JEE Mains among \textbf{1.5M} candidates.
        \item Secured an All India Rank of \textbf{52} out of 50k in Undergraduate Common Entrance Examination for Design.
    \end{itemize}
    }
    \vspace{\vEduSkills}
    \textbf{Skills} : Python, C++, ROS/ROS2, MoveIt, MuJoCo, Gazebo, PyTorch, JAX, OpenCV, Docker, URDF/SDF, CUDA
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\color{Blue}Professional Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Master's Thesis: Generative Motion Planning for Sim-to-Real Transfer}{Jan 2026 -- Jun 2026}{ABB Robotics}{V\"{a}ster\aa s, Sweden}
    \resumeItemListStart
        \resumeItem{Built a flow-matching planner guided by temporal-logic robustness gradients at inference without model retraining.}
        \resumeItem{Validated reach-avoid policies in MuJoCo; actively transferring to 6-DoF manipulation hardware with ABB R\&D.}
        \resumeItem{Benchmarked against specification-constrained planning baselines on 2D and continuous-control navigation tasks.}
    \resumeItemListEnd

    \resumeSubheading{Device Research Intern: 3D Scene Graphs}{Jul 2025 -- Dec 2025}{Ericsson Research}{Lund, Sweden}
    \resumeItemListStart
        \resumeItem{Integrated instance segmentation and tracking into Hydra, a real-time 3D scene-graph construction framework.}
        \resumeItem{Built a synchronized RGB-D inpainting pipeline that removes privacy-sensitive objects from scene graphs online.}
        \resumeItem{Benchmarked state-of-the-art inpainting models to balance reconstruction fidelity against real-time latency.}
    \resumeItemListEnd

    \resumeSubheading{Graduate Robotics Intern: Modular Collaborative Robots}{Dec 2022 -- Jul 2023}{Systemantics India}{Bangalore, India}
    \resumeItemListStart
        \resumeItem{Developed the real-time system controller from scratch for a 6-DoF cobot; deployed on PREEMPT RT Linux.}
        \resumeItem{Implemented 7-zone S-curve trajectory generation to smooth acceleration profiles and reduce mechanical shock.}
        \resumeItem{Authored URDFs and SRDFs for the cobot; integrated ROS2 with MoveIt2 motion planning and Gazebo simulation.}
        \resumeItem{Initiated impedance control for collision detection and kinesthetic teaching using a joint disturbance observer.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------RESEARCH-----------
\section{\color{Blue}Research Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Autonomous Ultrasound Scanning via 3D Surface Reconstruction}{Jan 2024 -- May 2024}{Nirav Patel, INSPIRE Lab, IIT Madras}{Chennai, India}
    \resumeItemListStart
        \resumeItem{Performed 3D torso surface reconstruction from 20 predefined RGB poses via multi-view stereo on a 5-DoF robot arm.}
        \resumeItem{Segmented the abdominal ROI from the point cloud and estimated probe approach angles from surface tangent vectors.}
        \resumeItem{Wired the reconstruction output into ROS/MoveIt motion planning and Gazebo simulation for end-to-end validation.}
    \resumeItemListEnd

    \resumeSubheading{Target-Tracking Motion Planning for UAVs}{Sep 2021 -- Apr 2022}{Prof. Satadal Ghosh, IIT Madras}{Chennai, India}
    \resumeItemListStart
        \resumeItem{Built 2D target-tracking and obstacle avoidance for UAVs via Proportional Navigation and velocity obstacles.}
        \resumeItem{Achieved \textasciitilde20\% faster trajectories with lower compute cost than classical aerospace motion planning algorithms.}
        \resumeItem{Awarded the IIT Madras Young Research Fellowship (top 30 of 800+ applicants) for outstanding research contribution.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\color{Blue}Technical Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading{EKF-SLAM and State Estimation $|$ \textnormal{\small EL2320, KTH}}{Mar 2025 -- Jun 2025}
    \resumeItemListStart
        \resumeItem{Implemented 2D EKF-SLAM from scratch with known and unknown data association via Mahalanobis distance gating.}
        \resumeItem{Extended filter state and covariance dynamically per new landmark discovery; resolved a matrix-consistency bug.}
        \resumeItem{Showed position error within 3\(\sigma\) under known association; divergence on symmetric maps revealed EKF overconfidence.}
    \resumeItemListEnd

    \resumeProjectHeading{Multi-Variable Dynamics Modeling and H$_\infty$ Control $|$ \textnormal{\small EL2520, KTH}}{Jan 2025 -- Mar 2025}
    \resumeItemListStart
        \resumeItem{Modeled a four-tank process from first principles; identified min- and non-min-phase regimes through RGA analysis.}
        \resumeItem{Designed a decentralized decoupling controller and a robust H$_\infty$ loop-shaping controller for the hydraulic process.}
        \resumeItem{Validated the H$_\infty$ controller: 4s rise time, 20\% overshoot, and 2\% steady-state error in the minimum-phase regime.}
    \resumeItemListEnd

    \resumeProjectHeading{Robot IK, Motion Planning, and Mapping $|$ \textnormal{\small DD2410, KTH}}{Sep 2024 -- Oct 2024}
    \resumeItemListStart
        \resumeItem{Solved analytic IK for a 3-DoF arm and Jacobian-based IK for a 7-DoF manipulator using DH parameterization.}
        \resumeItem{Implemented Hybrid A* and RRT for a Dubins car; generated collision-free paths around circular and line obstacles.}
        \resumeItem{Developed a Behavior Tree mission planner for autonomous navigation, grasping, and recovery in ROS/Gazebo.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS----------- (RULE 6: canonical block — copy verbatim from single-ref.tex)
\section{\color{Blue}Lead Author Publications}
\begin{itemize}[leftmargin=0.15in]
    \setlength{\itemsep}{\vPubSep}
    \item Robust Object-layer Construction of 3DSG Using Instance Segmentation (IMPROVE26)(\textbf{Best Paper Award})
    \item Synchronized RGB-D Inpainting for Privacy-Aware 3D Scene Graph Construction.(\textbf{ICPR26}).(Under Review)
    \item Scene Understanding in Deformable Object Manipulation via Taxonomy-Guided VLMs.(\textbf{IROS25} Workshop)
\end{itemize}

\end{document}
