%====================================================================================
%  single-FactoryAutomation.tex  —  Siemens Energy: Robotics & Factory Automation Expert
%  Tailored from single-ref.tex. Industry single-page resume. See CLAUDE.md sec 3.
%====================================================================================

\documentclass[letterpaper, 11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{vwcol}
\usepackage{comment}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=black,
	citecolor=black,
	urlcolor=Blue,
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% VSPACE VARIABLES (this file only) — tune layout spacing here.
% Categorized by document section, in order; cross-section macro vars in Global/Shared first.

% --- Global / Shared (drive macros used across every section) ---
\newcommand{\vSectionBefore}{-10pt} % space before each \section title
\newcommand{\vSectionRule}{-5pt}   % space after the blue section titlerule
\newcommand{\vTableRowSep}{-2pt}   % row strut between title/subtitle rows in resumeSubheading
\newcommand{\vItemTop}{-3pt}       % tightening atop resumeItem / subheading / project heading
\newcommand{\vSubheadingEnd}{-8pt}% space after a resumeSubheading block
\newcommand{\vSubItem}{-4pt}       % space after a resumeSubItem
\newcommand{\vListStart}{-0.3em}   % space before an item list start (resumeItemListStart / education list)
\newcommand{\vListEnd}{-3pt}       % space after resumeItemListEnd
\newcommand{\vListGroupEnd}{-1em}  % space after resumeSubHeadingListEnd

% --- Header ---
\newcommand{\vHeadingName}{3pt}    % space under the name in the header
\newcommand{\vHeadingEnd}{-3pt}    % space after the header block

% --- Summary ---
\newcommand{\vSummaryTop}{0pt}     % space atop the summary text
\newcommand{\vSummaryEnd}{-6pt}    % space after the summary text

% --- Education ---
\newcommand{\vEduSep}{3pt}         % space between education entries
\newcommand{\vEduItemSep}{-0.3em}  % itemsep between Education achievement bullets
\newcommand{\vEduSkills}{-0.7em}   % space before the education Skills line

% --- Technical Projects ---
\newcommand{\vProjectEnd}{-15pt}   % space after a resumeProjectHeading block

% --- Publications ---
\newcommand{\vPubSep}{-2pt}        % itemsep between Publications entries

% Sections formatting
\titleformat{\section}{ \vspace{\vSectionBefore}\scshape\raggedright\large\bfseries }{}{0em}{}[
\color{Blue}{}
\titlerule
\vspace{\vSectionRule}
]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{ \item\small{ {#1 \vspace{\vItemTop}} } }

\newcommand{\resumeSubheading}[4]{
\vspace{\vItemTop}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}       & {\small #2} \\
     [\vTableRowSep]
	\textit{{\small#3}} & \textit{\small #4} \\
\end{tabular*}
\vspace{\vSubheadingEnd}
}

\newcommand{\resumeProjectHeading}[2]{
\vspace{\vItemTop}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}  & {\small #2} \\
\end{tabular*}
\vspace{\vProjectEnd}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}
\vspace{\vSubItem}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{\vListGroupEnd}}
\newcommand{\resumeItemListStart}{\vspace{\vListStart}\begin{itemize}[leftmargin=0.25in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{\vListEnd}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Gawtam Chithra Ramesh} \\
    \vspace{\vHeadingName}
    \small
    { \href{tel:+46764518589}{{\faMobile*} \textcolor{black}{(+46) 76541-8589}} ~
    \href{mailto:gawtamcr3@gmail.com}{{\faPaperPlane} \textcolor{black}{gawtamcr3@gmail.com}} ~
    \href{https://linkedin.com/in/gawtamcr/}{{\faLinkedinIn} \textcolor{black}{Gawtam C R}} ~
    \href{https://github.com/gawtamcr}{{\faGithub} \textcolor{black}{gawtamcr}} ~
    \href{https://gawtamcr.github.io/}{{\faGlobe} \textcolor{black}{Portfolio}} ~
    \href{https://maps.google.com/?q=Stockholm,Sweden}{{\faMapMarker*} \textcolor{black}{Stockholm, Sweden}}
    }
    \vspace{\vHeadingEnd}
\end{center}

%-----------SUMMARY----------- (tailored per role; counts toward 30-line floor)
\section{\color{Blue}Summary}
\vspace{\vSummaryTop}
\small{Robotics engineer (MSc, KTH) with hands-on experience deploying industrial robots and cobots in production, from real-time controllers and trajectory generation to ROS-based motion planning. Combines factory automation with computer vision and adaptive AI to improve safety, quality, and productivity, balancing near-term delivery with exploration of emerging physical-AI technology.}
\vspace{\vSummaryEnd}

%-----------EDUCATION-----------
\section{\color{Blue}Education}
    \resumeSubHeadingListStart
    \resumeSubheading{KTH Royal Institute of Technology}{Aug 2024 -- Jun 2026}{Master of Science in Systems, Controls, and Robotics \textnormal{(GPA 4.62/5.0)}}{Stockholm, Sweden}
    \vspace{\vEduSep}
    \resumeSubheading{Indian Institute of Technology Madras}{Aug 2019 -- Jul 2024}{Dual Degree (B.Tech Engineering Design and M.Tech Robotics) \textnormal{(GPA 7.9/10)}}{Chennai, India}
    \vspace{\vListStart}
    \small{
    \begin{itemize}[leftmargin=0.15in]
        \setlength{\itemsep}{\vEduItemSep}
        \item Awarded (among 30 of 800+) the IIT Madras \textbf{Young Research Fellowship} based on remarkable research potential.
        \item Secured \textbf{97.64} Percentile in JEE Advanced and \textbf{99.10} Percentile in JEE Mains among \textbf{1.5M} candidates.
        \item Secured an All India Rank of \textbf{52} out of 50k in Undergraduate Common Entrance Examination for Design.
    \end{itemize}
    }
    \vspace{\vEduSkills}
    \textbf{Skills} : Python, C++, ROS/ROS2, MoveIt, Gazebo, MuJoCo, PyTorch, OpenCV, Behavior Trees, Docker, CUDA, MATLAB
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\color{Blue}Professional Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Master's Thesis: Generative Planning for Industrial Manipulation}{Jan 2026 -- Jun 2026}{ABB Robotics}{V\"{a}ster\aa s, Sweden}
    \resumeItemListStart
        \resumeItem{Designed a generative flow-matching motion planner for industrial manipulation steered by formal task goals.}
        \resumeItem{Steered the pretrained planner to new task constraints at inference without retraining for fast redeployment.}
    \resumeItemListEnd

    \resumeSubheading{Device Research Intern: 3D Scene Graphs}{Jul 2025 -- Dec 2025}{Ericsson Research}{Lund, Sweden}
    \resumeItemListStart
        \resumeItem{Integrated instance segmentation and tracking into Hydra, a real-time 3D scene-graph perception framework.}
        \resumeItem{Built a synchronized RGB-D inpainting pipeline that removes privacy-sensitive objects from scene graphs online.}
        \resumeItem{Benchmarked state-of-the-art vision models to balance reconstruction fidelity against real-time inference latency.}
    \resumeItemListEnd

    \resumeSubheading{Graduate Robotics Intern: Collaborative Robots}{Dec 2022 -- Jul 2023}{Systemantics India}{Bangalore, India}
    \resumeItemListStart
        \resumeItem{Built a complete real-time system controller from scratch for a 6-DoF collaborative robot on Linux PREEMPT-RT.}
        \resumeItem{Generated jerk-limited S-curve trajectories that cut mechanical shock via smooth acceleration and deceleration.}
        \resumeItem{Engineered behavior-tree task planning and ROS2 MoveIt motion planning for long-horizon pipetting and inspection.}
    \resumeItemListEnd

    \resumeSubheading{Robotics Intern: Pallet Handling}{Jun 2021 -- Jul 2021}{Yaskawa}{Gurgaon, India}
    \resumeItemListStart
        \resumeItem{Modeled 3D palletizing layouts for mixed-size cartons on an industrial robot using offline simulation tooling.}
        \resumeItem{Programmed pick-and-place sequences on the teach pendant and validated reachability across varied carton stacks.}
        \resumeItem{Wrote a C++ routine to optimize controller memory while streaming motion data from a PC to the robot controller.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------RESEARCH-----------
\section{\color{Blue}Research Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Autonomous Ultrasound Scanning from a Single RGB Camera}{Jan 2024 -- May 2024}{\href{https://ed.iitm.ac.in/}{Nirav Patel}, INSPIRE Lab, IIT Madras}{Chennai, India}
    \resumeItemListStart
        \resumeItem{Reconstructed a dense 3D torso point cloud from one RGB camera via structure-from-motion and multi-view stereo.}
        \resumeItem{Segmented the abdominal region from the point cloud and estimated surface tangents for the probe approach angle.}
        \resumeItem{Closed a perception-to-planning loop with ROS and MoveIt motion planning validated in physics simulation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\color{Blue}Technical Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading{Robot Learning and Embodied AI $|$ \textnormal{\small DD2600, KTH}}{Aug 2025 -- Oct 2025}
    \resumeItemListStart
        \resumeItem{Built a vision-language pipeline mapping RGB-D frames to 3D semantic voxel maps for queryable object presence.}
        \resumeItem{Trained a ResNet classifier on ~2,000 heatmap samples, reaching 86.2\% validation accuracy and 0.917 ROC-AUC.}
    \resumeItemListEnd

    \resumeProjectHeading{Image Analysis and Computer Vision $|$ \textnormal{\small DD2423, KTH}}{Oct 2024 -- Jan 2025}
    \resumeItemListStart
        \resumeItem{Implemented edge detection via differential-geometry zero-crossings and a Hough-transform line detector.}
        \resumeItem{Built SIFT feature matching with RANSAC homography estimation for robust planar-scene alignment.}
        \resumeItem{Estimated the fundamental matrix and triangulated 3D points from calibrated camera projection matrices.}
    \resumeItemListEnd

    \resumeProjectHeading{Introduction to Robotics $|$ \textnormal{\small DD2410, KTH}}{Sep 2024 -- Oct 2024}
    \resumeItemListStart
        \resumeItem{Implemented analytic and Jacobian-based inverse kinematics for 3-DoF and 7-DoF manipulators, passing all tests.}
        \resumeItem{Built a 2D occupancy-grid mapper from laser scans with raytraced free space and configuration-space inflation.}
        \resumeItem{Designed a behavior-tree mission planner for a mobile manipulator performing vision-based grasping in simulation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{\color{Blue}Lead Author Publications}
\begin{itemize}[leftmargin=0.15in]
    \setlength{\itemsep}{\vPubSep}
    \item Robust Object-layer Construction of 3DSG Using Instance Segmentation (IMPROVE26)(\textbf{Best Paper Award})
    \item Synchronized RGB-D Inpainting for Privacy-Aware 3D Scene Graph Construction.(\textbf{ICPR26}).(Under Review)
    \item Scene Understanding in Deformable Object Manipulation via Taxonomy-Guided VLMs.(\textbf{IROS25} Workshop)
\end{itemize}

\end{document}
