\documentclass[letterpaper, 11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{vwcol}
\usepackage{comment}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=black,
	citecolor=black,
	urlcolor=Blue,
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{ \vspace{-4pt}\scshape\raggedright\large\bfseries }{}{0em}{}[
\color{Blue}{}
\titlerule
\vspace{-5pt}
]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{ \item\small{ {#1 \vspace{-2pt}} } }

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}       & {\small #2} \\
     [-2pt]
	\textit{{\small#3}} & \textit{\small #4} \\
\end{tabular*}
\vspace{-10pt}
}

\newcommand{\resumeProjectHeading}[2]{
\vspace{-2pt}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}  & {\small #2} \\
\end{tabular*}
\vspace{-18pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}
\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-1em}}
\newcommand{\resumeItemListStart}{\vspace{-0.3em}\begin{itemize}[leftmargin=0.25in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7.5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Gawtam Chithra Ramesh} \\
    \vspace{3pt}
    \small
    { \href{tel:+46764518589}{{\faMobile*} \textcolor{black}{(+46) 76541-8589}} ~
    \href{mailto:gawtamcr3@gmail.com}{{\faPaperPlane} \textcolor{black}{gawtamcr3@gmail.com}} ~
    \href{https://linkedin.com/in/gawtamcr/}{{\faLinkedinIn} \textcolor{black}{Gawtam C R}} ~
    \href{https://github.com/gawtamcr}{{\faGithub} \textcolor{black}{gawtamcr}} ~
    \href{https://gawtamcr.github.io/}{{\faGlobe} \textcolor{black}{Portfolio}} ~
    \href{https://maps.google.com/?q=Stockholm,Sweden}{{\faMapMarker*} \textcolor{black}{Stockholm, Sweden}}
    }
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{\color{Blue}Education}
    \resumeSubHeadingListStart
    \resumeSubheading{KTH Royal Institute of Technology}{Aug 2024 -- Jun 2026}{Master of Science in Systems, Controls, and Robotics \textnormal{(GPA 4.62/5.0)}}{Stockholm, Sweden}
    \resumeSubheading{Indian Institute of Technology Madras}{Aug 2019 -- Jul 2024}{Dual Degree (B.Tech Engineering Design and M.Tech Robotics) \textnormal{(GPA 7.9/10)}}{Chennai, India}
    \vspace{-0.3em}
    \small{
    \begin{itemize}[leftmargin=0.15in]
        \setlength{\itemsep}{-0.3em}
        \item Awarded (among 30 of 800+) the IIT Madras \textbf{Young Research Fellowship} based on remarkable research potential.
        \item Secured \textbf{97.64} Percentile in JEE Advanced and \textbf{99.10} Percentile in JEE Mains among \textbf{1.5M} candidates.
        \item Secured an All India Rank of \textbf{52} out of 50k in Undergraduate Common Entrance Examination for Design.
    \end{itemize}
    }
    \vspace{-0.7em}
    \textbf{Skills} : Python, C++, C\texttt{\#}, PyTorch, JAX, CUDA, Slurm, ROS2, MuJoCo, PyBullet, OpenCV, wandb, Docker, Git
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\color{Blue}Professional Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Master's Thesis: Generative Flow Matching for Robot Manipulation}{Jan 2026 -- Jun 2026}{ABB Robotics}{V\"{a}ster\aa s, Sweden}
    \resumeItemListStart
        \resumeItem{Designed a generative flow-matching trajectory planner guided at inference by Signal Temporal Logic gradients.}
        \resumeItem{Steered a single pretrained flow model toward unseen temporal-logic specifications at inference without retraining.}
        \resumeItem{Benchmarked on long-horizon reach-avoid navigation against state-of-the-art specification-guided generative planners.}
    \resumeItemListEnd

    \resumeSubheading{Device Research Intern: 3D Scene Graphs}{Jul 2025 -- Dec 2025}{Ericsson Research}{Lund, Sweden}
    \resumeItemListStart
        \resumeItem{Integrated instance segmentation and tracking into Hydra, a real-time 3D scene-graph construction framework.}
        \resumeItem{Built a synchronized RGB-D inpainting pipeline that removes privacy-sensitive objects from scene graphs online.}
        \resumeItem{Benchmarked state-of-the-art generative inpainting models to balance reconstruction fidelity against real-time latency.}
    \resumeItemListEnd

    \resumeSubheading{Multi-Object Detection \& Tracking Intern}{Jun 2021 -- Jul 2021}{Blurgs Research Labs}{Remote, India}
    \resumeItemListStart
        \resumeItem{Evaluated five state-of-the-art multi-object tracking architectures for an Indian Navy video-surveillance product.}
        \resumeItem{Trained deep detection-and-tracking models on aerial drone and CCTV footage for real-time multi-target tracking.}
        \resumeItem{Deployed the top model for online tracking and re-identification of multiple moving targets across video streams.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------RESEARCH-----------
\section{\color{Blue}Research Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Taxonomy-Guided Vision-Language Models for Manipulation}{Jan 2025 -- Nov 2025}{\href{https://www.kth.se/is/rpl}{Prof. Florian T. Pokorny}, Robotics, Perception \& Learning Lab, KTH}{Stockholm, Sweden}
    \resumeItemListStart
        \resumeItem{Coupled vision-language foundation models with a taxonomy to interpret deformable-object manipulation scenes.}
        \resumeItem{Built a prompt-taxonomy framework mapping natural language to robot-parsable structured motion primitives.}
        \resumeItem{Quantified taxonomy-grounding and natural-language correctness with F1-score and text-similarity metrics.}
    \resumeItemListEnd

    \resumeSubheading{Autonomous Ultrasound Scan via Structure-from-Motion}{Jan 2024 -- May 2024}{\href{https://niravatgit.github.io/patelnirav.com/index.html}{Prof. Nirav Patel}, Department of Engineering Design, IIT Madras}{Chennai, India}
    \resumeItemListStart
        \resumeItem{Reconstructed a dense 3D torso point cloud from uncalibrated monocular RGB images via structure-from-motion.}
        \resumeItem{Densified the reconstruction with multi-view stereo and published the surface as a ROS point-cloud message.}
        \resumeItem{Segmented the abdominal region and estimated surface normals to plan the probe approach in a ROS/MoveIt pipeline.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\color{Blue}Technical Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading{Deep Learning Advanced $|$ \textnormal{\small DD2610, KTH}}{Nov 2025 -- Jan 2026}
    \resumeItemListStart
        \resumeItem{Reimplemented a one-step generative flow-matching model in PyTorch, ablating its time-sampling schedule and ratios.}
        \resumeItem{Showed accuracy-based generative quality metrics break down under classifier-free guidance mixing at sampling time.}
        \resumeItem{Built a Masked Autoencoder ViT from scratch with an asymmetric encoder-decoder and 75\% random patch masking.}
        \resumeItem{Pretrained a contrastive self-supervised encoder, reaching 86\% linear accuracy on CIFAR-10 using only 1\% labels.}
    \resumeItemListEnd

    \resumeProjectHeading{3D Open-Vocabulary Semantic Mapping $|$ \textnormal{\small DD2600 Robot Learning, KTH}}{Aug 2025 -- Oct 2025}
    \resumeItemListStart
        \resumeItem{Built a CLIP-based semantic voxel-mapping pipeline from RGB-D scans for open-vocabulary object-presence detection.}
        \resumeItem{Fused open-vocabulary detection with promptable segmentation to ground object instances in a 3D voxel map.}
        \resumeItem{Trained a ResNet18 presence classifier from scratch, reaching 86.2\% validation accuracy and 0.917 ROC-AUC.}
    \resumeItemListEnd

    \resumeProjectHeading{Artificial Intelligence \& Multi-Agent Systems $|$ \textnormal{\small DD2438, KTH}}{Feb 2025 -- May 2025}
    \resumeItemListStart
        \resumeItem{Coordinated 20+ holonomic and non-holonomic agents collision-free using conflict-based multi-agent path-finding.}
        \resumeItem{Trained three role-specific PPO policies for attack, defend, and escape in a multi-agent capture-the-flag game.}
        \resumeItem{Fused a behavior tree with reinforcement learning via self-play and curriculum training across staged episodes.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{\color{Blue}Lead Author Publications}
\begin{itemize}[leftmargin=0.15in]
    \setlength{\itemsep}{-5pt}
    \item Robust Object-layer Construction of 3DSG Using Instance Segmentation (IMPROVE26)(\textbf{Best Paper Award})
    \item Synchronized RGB-D Inpainting for Privacy-Aware 3D Scene Graph Construction.(\textbf{ICPR26}).(Under Review)
    \item Scene Understanding in Deformable Object Manipulation via Taxonomy-Guided VLMs.(\textbf{IROS25} Workshop)
\end{itemize}

\end{document}
