%====================================================================================
%  single-FieldRobotics.tex  —  KTH Research Engineer, Robotic Systems for Aerial &
%  Underwater Domains (I-SEE project). Seeded from single-ref.tex. See CLAUDE.md sec 3.
%====================================================================================

\documentclass[letterpaper, 11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{vwcol}
\usepackage{comment}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=black,
	citecolor=black,
	urlcolor=Blue,
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{ \vspace{-4pt}\scshape\raggedright\large\bfseries }{}{0em}{}[
\color{Blue}{}
\titlerule
\vspace{-5pt}
]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{ \item\small{ {#1 \vspace{-2pt}} } }

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}       & {\small #2} \\
     [-2pt]
	\textit{{\small#3}} & \textit{\small #4} \\
\end{tabular*}
\vspace{-10pt}
}

\newcommand{\resumeProjectHeading}[2]{
\vspace{-2pt}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}  & {\small #2} \\
\end{tabular*}
\vspace{-18pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}
\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-1em}}
\newcommand{\resumeItemListStart}{\vspace{-0.3em}\begin{itemize}[leftmargin=0.25in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8.5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Gawtam Chithra Ramesh} \\
    \vspace{3pt}
    \small
    { \href{tel:+46764518589}{{\faMobile*} \textcolor{black}{(+46) 76541-8589}} ~
    \href{mailto:gawtamcr3@gmail.com}{{\faPaperPlane} \textcolor{black}{gawtamcr3@gmail.com}} ~
    \href{https://linkedin.com/in/gawtamcr/}{{\faLinkedinIn} \textcolor{black}{Gawtam C R}} ~
    \href{https://github.com/gawtamcr}{{\faGithub} \textcolor{black}{gawtamcr}} ~
    \href{https://gawtamcr.github.io/}{{\faGlobe} \textcolor{black}{Portfolio}} ~
    \href{https://maps.google.com/?q=Stockholm,Sweden}{{\faMapMarker*} \textcolor{black}{Stockholm, Sweden}}
    }
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{\color{Blue}Education}
    \resumeSubHeadingListStart
    \resumeSubheading{KTH Royal Institute of Technology}{Aug 2024 -- Jun 2026}{Master of Science in Systems, Controls, and Robotics \textnormal{(GPA 4.62/5.0)}}{Stockholm, Sweden}
    \resumeSubheading{Indian Institute of Technology Madras}{Aug 2019 -- Jul 2024}{Dual Degree (B.Tech Engineering Design and M.Tech Robotics) \textnormal{(GPA 7.9/10)}}{Chennai, India}
    \vspace{-0.3em}
    \small{
    \begin{itemize}[leftmargin=0.15in]
        \setlength{\itemsep}{-0.3em}
        \item Awarded (among 30 of 800+) the IIT Madras \textbf{Young Research Fellowship} based on remarkable research potential.
        \item Secured \textbf{97.64} Percentile in JEE Advanced and \textbf{99.10} Percentile in JEE Mains among \textbf{1.5M} candidates.
        \item Secured an All India Rank of \textbf{52} out of 50k in Undergraduate Common Entrance Examination for Design.
    \end{itemize}
    }
    \vspace{-0.7em}
    \textbf{Skills} : Python, C++, C, ROS2, MoveIt, Gazebo, Embedded Systems, PREEMPT-RT, SocketCAN, PyTorch, Unity3D, Fusion360, Docker, Git
    \resumeSubHeadingListEnd

%-----------EXPERIENCE----------- (\vspace pulls this header up to match the other section gaps;
% Education ends with a Skills text line, not a bullet list, so it leaves a larger natural gap.)
\vspace{-9pt}
\section{\color{Blue}Professional Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Master's Thesis: Generative Flow Matching for Motion Planning}{Jan 2026 -- Jun 2026}{ABB Robotics}{V\"{a}ster\aa s, Sweden}
    \resumeItemListStart
        \resumeItem{Designed a generative flow-matching planner guided at inference by Signal Temporal Logic robustness gradients.}
        \resumeItem{Steered the pretrained flow model toward new temporal-logic specifications at inference without retraining.}
        \resumeItem{Benchmarked on long-horizon reach-avoid navigation against state-of-the-art specification-guided motion planners.}
    \resumeItemListEnd

    \resumeSubheading{Device Research Intern: 3D Scene Graphs}{Jul 2025 -- Dec 2025}{Ericsson Research}{Lund, Sweden}
    \resumeItemListStart
        \resumeItem{Integrated instance segmentation and tracking into Hydra, a real-time 3D scene-graph construction framework.}
        \resumeItem{Built a synchronized RGB-D inpainting pipeline that removes privacy-sensitive objects from scene graphs online.}
        \resumeItem{Benchmarked state-of-the-art inpainting models to balance reconstruction fidelity against real-time edge latency.}
    \resumeItemListEnd

    \resumeSubheading{Graduate Robotics Intern: Collaborative Robots}{Dec 2022 -- Jul 2023}{Systemantics India}{Bangalore, India}
    \resumeItemListStart
        \resumeItem{Built a complete real-time system controller from scratch for a 6-DoF cobot portfolio on a Linux PREEMPT-RT kernel.}
        \resumeItem{Handled inter-process communication over SocketCAN and FDCAN buses using semaphores and signal interrupts.}
        \resumeItem{Integrated a ROS2 stack with MoveIt2 motion planning and Gazebo simulation, authoring URDF and SRDF descriptions.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------RESEARCH----------- (\vspace matches this header's gap to the others.)
\vspace{-12pt}
\section{\color{Blue}Research Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Autonomous Ultrasound via Single-Camera 3D Reconstruction}{Jan 2024 -- May 2024}{Nirav Patel, Engineering Design, IIT Madras}{Chennai, India}
    \resumeItemListStart
        \resumeItem{Reconstructed a dense 3D torso point cloud from 20 RGB poses via structure-from-motion and multi-view stereo.}
        \resumeItem{Segmented the reconstructed point cloud to estimate probe approach angles from local surface tangent vectors.}
        \resumeItem{Closed the perception-to-planning loop with ROS and MoveIt motion planning validated in Gazebo physics simulation.}
    \resumeItemListEnd

    \resumeSubheading{Target-Driven UAV Motion Planning and Obstacle Avoidance}{Sep 2021 -- Apr 2022}{Prof. Satadal Ghosh, Aerospace Engineering, IIT Madras}{Chennai, India}
    \resumeItemListStart
        \resumeItem{Developed target-driven motion planning with real-time obstacle avoidance for autonomous unmanned aerial vehicles.}
        \resumeItem{Combined Proportional Navigation with Acceleration-Velocity Obstacles for reactive 2D guidance toward moving targets.}
        \resumeItem{Achieved roughly 20\% faster and more compute-efficient trajectories than classical aerospace guidance algorithms.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\color{Blue}Technical Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading{Multi-Agent Path Finding and Coordination $|$ \textnormal{\small DD2438, KTH}}{Feb 2025 -- May 2025}
    \resumeItemListStart
        \resumeItem{Coordinated 20+ holonomic drones and non-holonomic cars with Conflict-Based Search over a Hybrid A* planner.}
        \resumeItem{Designed a greedy goal-assignment heuristic minimizing combined travel and assignment cost across the fleet.}
        \resumeItem{Added goal-padding and node-pruning heuristics with a fail-safe expansion bound for robust large-team planning.}
    \resumeItemListEnd

    \resumeProjectHeading{Autonomous Mobile Manipulation Stack $|$ \textnormal{\small DD2410, KTH}}{Sep 2024 -- Oct 2024}
    \resumeItemListStart
        \resumeItem{Built a Behavior Tree mission planner for a mobile manipulator handling navigation, grasping, and recovery in ROS.}
        \resumeItem{Implemented Hybrid A* and RRT planners for a Dubins car with collision checking against line and circle obstacles.}
        \resumeItem{Generated 2D occupancy grids from laser scans with raytraced free space and configuration-space inflation.}
    \resumeItemListEnd

    \resumeProjectHeading{Hyperloop Pod Battery Pack and BMS $|$ \textnormal{\small Avishkar Hyperloop, IIT Madras}}{Oct 2020 -- Jun 2021}
    \resumeItemListStart
        \resumeItem{Designed a high-discharge battery pack, extending pack life 10\% by cutting peak temperature 10C with aluminium sinks.}
        \resumeItem{Built a custom Battery Management System for real-time voltage and temperature monitoring with safety cutoffs.}
        \resumeItem{Won the Most Scalable Design award and reached the top 24 teams for European Hyperloop Week in Valencia, Spain.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{\color{Blue}Lead Author Publications}
\begin{itemize}[leftmargin=0.15in]
    \setlength{\itemsep}{-5pt}
    \item Robust Object-layer Construction of 3DSG Using Instance Segmentation (IMPROVE26)(\textbf{Best Paper Award})
    \item Synchronized RGB-D Inpainting for Privacy-Aware 3D Scene Graph Construction.(\textbf{ICPR26}).(Under Review)
    \item Scene Understanding in Deformable Object Manipulation via Taxonomy-Guided VLMs.(\textbf{IROS25} Workshop)
\end{itemize}

\end{document}
