\documentclass[letterpaper, 11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{vwcol}
\usepackage{comment}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=black,
	citecolor=black,
	urlcolor=Blue,
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[
\color{Blue}{}\titlerule\vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1} & {\small #2} \\[-2pt]
	\textit{{\small#3}} & \textit{\small #4} \\
\end{tabular*}
\vspace{-10pt}
}

\newcommand{\resumeProjectHeading}[2]{
\vspace{-2pt}\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1} & {\small #2} \\
\end{tabular*}
\vspace{-18pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-1em}}
\newcommand{\resumeItemListStart}{\vspace{-0.3em}\begin{itemize}[leftmargin=0.25in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5.0pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Gawtam Chithra Ramesh} \\
    \vspace{3pt}
    \small
    \href{tel:+46764518589}{{\faMobile*} \textcolor{black}{(+46) 76541-8589}} ~
    \href{mailto:gawtamcr3@gmail.com}{{\faPaperPlane} \textcolor{black}{gawtamcr3@gmail.com}} ~
    \href{https://linkedin.com/in/gawtamcr/}{{\faLinkedinIn} \textcolor{black}{gawtamcr}} ~
    \href{https://github.com/gawtamcr}{{\faGithub} \textcolor{black}{gawtamcr}} ~
    \href{https://gawtamcr.github.io/}{{\faGlobe} \textcolor{black}{Portfolio}} ~
    \href{https://maps.google.com/?q=Stockholm,Sweden}{{\faMapMarker*} \textcolor{black}{Stockholm, Sweden}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{\color{Blue}Education}
\resumeSubHeadingListStart
    \resumeSubheading{KTH Royal Institute of Technology}{Aug 2024 -- Jun 2026}{MSc Systems, Controls \& Robotics \textnormal{-- GPA 4.62/5.0}}{Stockholm, Sweden}
    \resumeSubheading{Indian Institute of Technology Madras}{Aug 2019 -- Jun 2024}{Dual Degree B.Tech Engineering Design + M.Tech Robotics \textnormal{-- GPA 7.9/10}}{Chennai, India}
    \vspace{-0.3em}
    \small{
    \begin{itemize}[leftmargin=0.15in]
        \setlength{\itemsep}{-0.3em}
        \item Awarded (among 30 of 800+) the IIT Madras \textbf{Young Research Fellowship} based on research potential.
        \item Secured \textbf{97.64} percentile JEE Advanced; \textbf{All India Rank 52} in UCEED among 50,000+ candidates.
    \end{itemize}
    }
    \vspace{-0.7em}
    \textbf{Skills}: Python, C++, PyTorch, JAX, OpenCV, YOLO, ROS/ROS2, MuJoCo, PyBullet, MATLAB, Docker, Git
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\color{Blue}Professional Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Device Research Intern -- 3D Scene Graphs}{Jul 2025 -- Dec 2025}{Ericsson Research}{Lund, Sweden}
    \resumeItemListStart
        \resumeItem{Integrated instance segmentation + tracking into Hydra (SOTA 3DSG framework) for robust scene interpretation.}
        \resumeItem{Built RGB-D inpainting pipeline to remove privacy-sensitive objects from 3D scene graphs in real time.}
        \resumeItem{Benchmarked SOTA inpainting methods on reconstruction fidelity vs.\ real-time performance trade-off.}
        \resumeItem{\textbf{Lead author:} IMPROVE 2026 (Long Oral, Best Paper nominee); ICPR 2026 (under review).}
    \resumeItemListEnd

    \resumeSubheading{Multi-Object Detection \& Tracking Intern}{Jun 2021 -- Jul 2021}{Blurgs Research Labs}{Remote, India}
    \resumeItemListStart
        \resumeItem{Analyzed 5 SOTA MOT networks for an Indian Navy drone/CCTV surveillance product.}
        \resumeItem{Trained Siam-MOT and FairMOT; deployed FairMOT for real-time multi-object tracking and re-ID.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------RESEARCH-----------
\section{\color{Blue}Research Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Taxonomy-Guided VLMs for Deformable Object Manipulation}{Jan 2025 -- Nov 2025}{KTH Robotics, Perception \& Learning Lab -- Advisor: Prof.\ Florian T.\ Pokorny}{Stockholm, Sweden}
    \resumeItemListStart
        \resumeItem{Integrated VLMs (GPT-4o, Gemini, Qwen) with T-DOM taxonomy to map scenes to robot motion primitives.}
        \resumeItem{Built prompt-taxonomy framework; evaluated with F1-Score, BERT, BLEU/ROUGE on taxonomy correctness.}
        \resumeItem{\textbf{Lead author:} ROMADO @ IROS 2025 (accepted); targeting IROS 2026 + IJRR full paper.}
    \resumeItemListEnd

    \resumeSubheading{Autonomous Ultrasound Scan via Structure-from-Motion}{Jan 2024 -- May 2024}{IIT Madras INSPIRE Lab -- Advisor: Prof.\ Nirav Patel}{Chennai, India}
    \resumeItemListStart
        \resumeItem{COLMAP SfM (monocular RGB, 20 poses) + OpenMVS dense reconstruction of human torso; no calibration needed.}
        \resumeItem{Point cloud segmentation (abdominal ROI) + surface normal estimation; ROS + MoveIt motion planning.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\color{Blue}Technical Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading{3D Open-Vocabulary Semantic Mapping $|$ \textnormal{\small DD2600 Robot Learning, KTH}}{2025}
    \resumeItemListStart
        \resumeItem{Object presence/absence detection in CLIP voxel maps (ARKitScenes; OwlV2 + SAM + CLIP pipeline).}
        \resumeItem{ResNet18 classifier: 86.2\% val accuracy, ROC-AUC 0.917; voxel-threshold baseline: 85\%, AUC 0.921.}
    \resumeItemListEnd

    \resumeProjectHeading{Image Analysis \& Computer Vision $|$ \textnormal{\small DD2423, KTH}}{2024}
    \resumeItemListStart
        \resumeItem{Gaussian FFT filtering; differential-geometry edge detection ($L_{vv}$/$L_{vvv}$ zero-crossings); Hough transform.}
        \resumeItem{SIFT + RANSAC for homography + fundamental matrix estimation; 3D reconstruction via triangulation.}
    \resumeItemListEnd

    \resumeProjectHeading{Deep Learning Advanced $|$ \textnormal{\small DD2610, KTH}}{2025}
    \resumeItemListStart
        \resumeItem{SimCLR: NTXent loss, ResNet18 + projection head, 86\% linear-eval accuracy on 1\% CIFAR-10 labels.}
        \resumeItem{MAE: ViT from scratch (PatchEmbed, multi-head attention, asymmetric encoder-decoder, 75\% masking).}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{\color{Blue}Lead Author Publications}
\begin{itemize}[leftmargin=0.15in]
    \setlength{\itemsep}{-4pt}
    \item Robust Object-layer Construction of 3D Scene Graphs Using Instance Segmentation. \textbf{IMPROVE 2026} (\textbf{Best Paper nominee}).
    \item Synchronized RGB-D Inpainting for Privacy-Aware 3D Scene Graph Construction. \textbf{ICPR 2026} (Under Review).
    \item Scene Understanding in Deformable Object Manipulation via Taxonomy-Guided VLMs. \textbf{IROS 2025}.
\end{itemize}

\end{document}
